Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-17 plosOne/SI/S1glossary.tex
adicionada primeiro arquivo do supporting information

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
 jmp,%
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\usepackage{hyperref}
\reserveinserts{58}
\usepackage{morefloats}
\usepackage[section]{placeins}
\usepackage{xcolor}
\usepackage{rotating}
%\usepackage{pdflscape}
\hypersetup{
        colorlinks,
            linkcolor={red!50!black},
                citecolor={blue!50!black},
                    urlcolor={blue!80!black}
                }

%%%%%%%%%%%%
\usepackage{listings}
\usepackage{xcolor}       
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{light-gray}{rgb}{0.97,0.97,0.97}

\lstdefinelanguage{owlms}
    {morekeywords={xsd,owl,xml,dc,rdf,skos,description,PlainLiteral,int,float,
        some,only,value,min,exactly,max,and,or,not,
        Prefix,Ontology,Import,Individual,Facts,Types,Class,
        DataProperty,ObjectProperty,AnnotationProperty,Annotations,
        DifferentIndividuals,SubClassOf,EquivalentTo,DisjointWith,DisjointUnionOf,SubPropertyOf,DisjointClasses,DisjointProperties,
        Symmetric,Asymmetric,Reflexive,Irreflexive,Transitive,Functional,InverseFunctional,
        Characteristics,Range,Domain,Datatype},
     basicstyle=\scriptsize\ttfamily,
     backgroundcolor=\color{light-gray},
     keywordstyle=\color{blue},
     commentstyle=\color{gray},
     stringstyle=\color{dkgreen},
     numbers=left,
     numberstyle=\tiny\color{gray},
     stepnumber=1,
     numbersep=10pt,
     tabsize=2,
     showspaces=false,
     showstringspaces=false,
     breaklines=true,                           % wrap text
     sensitive=true,                            % keywords are case sensitive
     morecomment=[l][commentstyle]{\#},         % comment format
     morestring=[b]",                           % string format
literate=%
  {ã}{{\~a}}1
  {â}{{\^a}}1
  {õ}{{\~o}}1
  {á}{{\'a}}1
  {ú}{{\'u}}1
  {í}{{\'i}}1
  {é}{{\'e}}1
  {Ç}{{\c{C}}}1
  {Õ}{{\~O}}1
  {Ê}{{\^E}}1
  {ó}{{\'o}}1
  {à}{{\`a}}1
  {Â}{{\^A}}1
  {ô}{{\^o}}1
  {ê}{{\^e}}1
  {ç}{{\c{c}}}1
}

@@

@@

@@

\newpage
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file aipsamp.tex ******

>>>>

\documentclass{article}
\newcommand{\ops}{\textsc{ops}}
\newcommand{\opsi}{O\textsc{ps}}
\newcommand{\vcps}{\textsc{vcps}}
\newcommand{\owl}{\textsc{owl}}
\newcommand{\owli}{O\textsc{wl}}
\newcommand{\sparql}{\textsc{s}par\textsc{ql}}
\newcommand{\bfo}{\textsc{bfo}}
\newcommand{\dbpedia}{\textsc{db}pedia}
\newcommand{\foaf}{\textsc{foaf}}
\newcommand{\ict}{\textsc{ict}}
\newcommand{\html}{\textsc{html}}
\newcommand{\node}{\textsc{n}ode.js}
\newcommand{\facebook}{\textsc{f}acebook}
\newcommand{\twitter}{\textsc{t}witter}
\newcommand{\wwwc}{\textsc{w3c}}
\newcommand{\skos}{\textsc{skos}}
\newcommand{\etherpad}{\textsc{e}therpad}
\newcommand{\ogp}{\textsc{ogp}}
\newcommand{\iri}{\textsc{iri}}
\newcommand{\uri}{\textsc{uri}}
\newcommand{\urii}{U\textsc{ri}}
\newcommand{\urll}{\textsc{url}}
\newcommand{\ngo}{\textsc{ngo}}
\newcommand{\http}{\textsc{http}}
\newcommand{\opa}{\textsc{op}a}
\newcommand{\ocd}{\textsc{ocd}}
\newcommand{\ontologiaa}{\textsc{o}ntologiaa}
\newcommand{\obs}{\textsc{obs}}
\newcommand{\pubby}{\textsc{p}ubby}
\newcommand{\rdf}{\textsc{rdf}}
\newcommand{\mysql}{\textsc{m}y\textsc{sql}}
\newcommand{\aan}{\textsc{aa}}
\newcommand{\cidadedemocratica}{\textsc{c}idade \textsc{d}emocr\'atica}
\newcommand{\participa}{\textsc{p}articipa.br}
\newcommand{\ontop}{\textsc{o}n\textsc{t}op}
\newcommand{\quest}{\textsc{q}uest}
\newcommand{\webprotege}{\textsc{w}ebprotege}
\newcommand{\obda}{\textsc{obda}}
\newcommand{\pnud}{\textsc{undp}}
\newcommand{\onu}{\textsc{un}}
\newcommand{\vbs}{\textsc{vbs}}
\newcommand{\lod}{\textsc{lod}}
\newcommand{\corais}{\textsc{c}orais}
\newcommand{\serpro}{\textsc{s}erpro}
\newcommand{\python}{\textsc{p}ython}
\newcommand{\protege}{\textsc{p}rot\`eg\`e}

\usepackage[margin=1em]{geometry}

@@

%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.

@@

%\end{adjustwidth}

@@

\end{document}
